Specifgic Gene or Metabolite Levels

### 2025-01-28 G85R GOandKEGGTermEnrichment.Rmd
serpe data

@@

subset = T

s1 = intersect(row.names(FDR[FDR[1] <.05,]), row.names(FC[FC[1] < 0,]))
s2 = intersect(row.names(FDR[FDR[2] <.05,]), row.names(FC[FC[2] < 0,]))
s3 = intersect(row.names(FDR[FDR[1] <.05,]), row.names(FC[FC[1] > 0,]))
s4 = intersect(row.names(FDR[FDR[2] <.05,]), row.names(FC[FC[2] > 0,]))

biomarkers = row.names(A4V.FDR[(A4V.FDR$AvS3FT > .05 &
                       A4V.FDR$AvS9FT > .05 &
                       A4V.FDR$AvS40FT < .05 &
                       A4V.FDR$AvS3MT > .05 &
                       A4V.FDR$AvS9MT < .05),])
expression.max = apply(A4V.meancpm[biomarkers, c("A40FT","S40FT","A9MT","S9MT")], MARGIN = 1, max)[biomarkers]
biomarkers = biomarkers[expression.max > 20]

NADmetab = names(kegg[grep('00760', kegg)])
biomarkers = row.names(GeneIDKey[GeneIDKey$Symbol %in% NADmetab, ])

if(subset == T){
  geneset = biomarkers
  s1 = intersect(s1, geneset)
  s2 = intersect(s2, geneset)
  s3 = intersect(s3, geneset)
  s4 = intersect(s4, geneset)
  FC[setdiff(row.names(FC),geneset),] = 1 
  FDR[setdiff(row.names(FDR),geneset),] = 1 
}

@@

```{r echo = F}
library(heatmaply)
hmdata = mean.data[geneset,]
row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
hmdata = na.omit(hmdata)

heatmaply(hmdata,
          scale = 'row',
          Colv = F)

>>>>

# Conditions
#Geno is WT or GR
#TKT is either "C", "OE", or "Df"
#Sex is "F" or "M"

Geno1 = "GR"
TKT1 = "C"
Sex1 = "F"

Geno2 = "WT"
TKT2 = "C"
Sex2 = "F"

temp.FC = colnames(G85R.FC)
temp1 = temp.FC[grep(Geno1, temp.FC)]

if(Sex1 != Sex2){
  temp1 = temp1[intersect(grep(Sex1, temp1), grep(Sex2, temp1))]
  temp1 = temp1[grep(Geno1)]
}

if(Sex1 == Sex2){
  if(Geno1 == Geno2){
  temp1 = temp1[grep(setdiff(c("WT", "GR"), c(Geno1, Geno2)), temp1, invert = T)]
  }

  if(Geno1 != Geno2){
  temp1 = temp1[intersect(grep(Geno1, temp1), grep(Geno2, temp1))]
  }

  temp1 = temp1[intersect(grep(TKT1, temp1), grep(TKT2, temp1))]

  temp1 = temp1[grep(Sex1, temp1)]
}

FC = G85R.FC[temp1]
FDR = G85R.FC[temp1]

@@

subset = F

if(subset == T){
  geneset = biomarkers
  FC[setdiff(row.names(FC),geneset),] = 1 
  FDR[setdiff(row.names(FDR),geneset),] = 1 
}

@@

```{r echo = F}
#library(heatmaply)
#hmdata = mean.data[geneset,]
#row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
#hmdata = na.omit(hmdata)

#heatmaply(hmdata,
#          scale = 'row',
#          Colv = F)

### 2025-01-28 GeneExpressionBoxPlots.Rmd
serpe data

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"

TKT.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)

TKT.groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

@@

A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv",row.names = 1)

A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")

gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
gbbOE = gbbOE[,row.names(gbbOE.groups)]
gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)

@@

gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)

@@

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

@@

@@

```{r echo = F}
##Function to plot all G85R groups

plot.G85R = function(ID){
ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]

@@

```{r echo = F}
##Function to plot a specific gene expression levels in all A4V groups

plot.A4V = function(ID){
ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]

if(nrow(ID.row) == 1){
  FBgn = ID.row$FBgn
  name = ID.row$Symbol
  A4V.groups = as.vector(colnames(A4V.cpm))

@@

```{r echo = F}
##Plot levels of a specific metabolite

plot.metab = function(metabID){

@@

if(length(ID.row) == 1){
metab = ID.row
name = ID.row

@@

@@

```{r echo = F}
##Tailared code to plot a specific gene expression levels in all A4V groups

@@

@@

@@

>>>>

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"

GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)

TKT.cpm = read.csv(paste0(git.dir,"TKT_cpmdata.csv"), row.names = 1)

TKT.groups  = read.csv(paste0(git.dir, "TKT.metadata.csv"), row.names = 1)

TKT.FDR = read.csv(paste0(git.dir, "TKT.EdgeR.FDRTable.csv"), row.names = 1)

TKT.FC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)

@@

A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)

A4V.FDR = read.csv(paste0(git.dir, "A4V.FDRdata.csv"), row.names = 1)

gbbOE = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)

gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)

gbbOE = gbbOE[,row.names(gbbOE.groups)]
gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)

@@

gbbKO = read.csv(paste0(git.dir, "gbbKO_CountTable.csv"), row.names = 1)

gbbKO.groups = read.csv(paste0(git.dir, "gbbKO_Metadata.csv"), row.names = 1)

@@

##write.csv(gbbKO.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/gbbKO.cpmdata.csv")

rawdata = read.csv(paste0(git.dir, "MetabolomicsForMetaboanalyst.txt"), sep = "\t", row.names = 1)

KEGG.Key = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)

KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

@@

SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"), row.names = 1)

@@

```{r echo = F}
##Function to plot all G85R groups
plot.G85R = function(ID){
ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
                     grep(ID, GeneIDKey$Symbol)),]

if(nrow(ID.row) < 500){
if(nrow(ID.row) == 1){
FBgn = ID.row$FBgn
name = ID.row$Symbol

@@

if(nrow(ID.row) != 1){
  ID.row
}
}
}

##Function to plot a specific gene expression levels in all A4V groups
plot.A4V = function(ID){
ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
                     grep(ID, GeneIDKey$Symbol)),]

if(nrow(ID.row) < 500){
if(nrow(ID.row) == 1){
  FBgn = ID.row$FBgn
  name = ID.row$Symbol
  A4V.groups = as.vector(colnames(A4V.cpm))

@@

if(nrow(ID.row) != 1){
  ID.row
}
}
}

##Plot levels of a specific metabolite
plot.metab = function(metabID){

@@

if(nrow(ID.row) < 500){
if(length(ID.row) == 1){
metab = ID.row
name = ID.row

@@

}
}

##Function to plot a specific gene expression levels in all cell types for the SCdata
plot.SC = function(gene.name){
ID.row = SCdata[grep(gene.name, SCdata$Gene.name),]

if(nrow(ID.row) < 500){
if(nrow(ID.row) == 1){

  gene.name = ID.row$Gene.name
  gene.levels = setNames(as.numeric(ID.row[,colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
  gene.levels = gene.levels[18:1]
  highlight = rep(0, 18)
  highlight[(gene.levels > 2*(mean(gene.levels)))] = 1
  highlight = gene.levels * highlight

  nochange = gene.levels
  nochange[gene.levels > 1.5] = 0
  nochange = gene.levels * nochange

  label.colors = highlight

  label.colors[label.colors > 0] = "deeppink"
  label.colors[label.colors == 0] = "black"
  label.colors[nochange > 0] = 'steelblue'

  if(1.25*(max(gene.levels)) < 5){
    xmax = 5
  }

  if(1.25*(max(gene.levels)) >= 5){
    xmax = 1.25*(max(gene.levels))
  }

  par(mar=c(5, 12, 4, 6), xpd=TRUE)

  plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(.95, 21),
     xlim = c(0, xmax),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = "Mean UMI Counts",
     bty = "n",
     main = gene.name)

  barplot(height = gene.levels, 
          horiz = T, 
          #las = 2,
          xlim = c(0, xmax),
          names.arg = NA,
          border = T,
          add = T)

    barplot(height = highlight, 
          horiz = T, 
          #las = 2, 
          names.arg = NA,
          border = T,
          col = "deeppink",
          add = T)

    barplot(height = nochange, 
          horiz = T, 
          #las = 2, 
          names.arg = NA,
          border = T,
          col = "lightsteelblue",
          add = T)

  mtext(side = 2,
        las = 2,
        at = .7+(1.2*(0:17)),
        text = names(gene.levels),
        col = label.colors,
        line = 0)

  abline(v = 1,
         lty = 2,
         lwd = 2,
         xpd = F)

  legend(x = .9*xmax,
         y = 23,
         legend = c("high", "mid", "low"),
         fill = c("deeppink", "grey", "lightsteelblue"),
         bty = "n",
         xpd = T)

@@

## Plot gene expression from A4V RNAseq experiment
## ID needs to be the full or partial gene symbol or FBgn (case sensitive)

@@

## Plot metabolite levels from the G85R TKT metabolomics experiment
## metabID needs to be the full or partial metabolite name as listed in the table (case sensitive)

@@

if(nrow(ID.row) < 500){
if(nrow(ID.row) == 1){
FBgn = ID.row$FBgn
name = ID.row$Symbol

@@

if(nrow(ID.row) < 500){
